My title

### 2024-03-12 paper/paper.qmd
Update paper.qmd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
date: today
date-format: long
abstract: 
There is no other nation in the world that conducts elections the way the United States does. Local government representatives oversee elections in around 8,000 distinct jurisdictions. They are then under the general supervision of authorities, who are frequently selected through election procedures or partisan appointees. Typically, the voter liaison at the polling place is a temporary worker who works unpaid for a single day and only gets a few hours of training. These distinctive characteristics of our electoral system, along with the fact that Americans vote more frequently than citizens in other countries on a wider range of issues and positions, create special difficulties for the efficient administration of elections that voters across demand and deserve.
None of the other nations' electoral systems display all or any of these traits, but none have the same mix of US administrative traits. The quality of administration differs from jurisdiction to jurisdiction and even from polling place to polling place because of decentralization and dependence on volunteers. Because partisan officials will be involved, accusations of partisanship regarding the rules or their interpretation may arise based on the outcome of the judgments made by the officials and who stands to gain from it. The quantity and variety of democratic options in protracted elections have outpaced voters' attention spans and cognitive capacities. These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections. This paper is mainly based on the 2022 US election.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

ces2022 |>
  ggplot(aes(x = race, fill = voted_for)) +
  stat_count(position = "dodge") +
  geom_text(stat='count', aes(label=..count..), position=position_dodge(width=0.9), vjust=-0.25, color="black") +
  facet_wrap(facets = vars(gender4)) +
  theme_minimal() +
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Dong Jun Yoon
  - Another author
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
date: today
date-format: long
abstract: 
There is no other nation in the world that conducts elections the way the United States does. Local government representatives oversee elections in around 8,000 distinct jurisdictions. They are then under the general supervision of authorities, who are frequently selected through election procedures or partisan appointees. Typically, the voter liaison at the polling place is a temporary worker who works unpaid for a single day and only gets a few hours of training. These distinctive characteristics of our electoral system, along with the fact that Americans vote more frequently than citizens in other countries on a wider range of issues and positions, create special difficulties for the efficient administration of elections that voters across demand and deserve.
None of the other nations' electoral systems display all or any of these traits, but none have the same mix of US administrative traits. The quality of administration differs from jurisdiction to jurisdiction and even from polling place to polling place because of decentralization and dependence on volunteers. Because partisan officials will be involved, accusations of partisanship regarding the rules or their interpretation may arise based on the outcome of the judgments made by the officials and who stands to gain from it. The quantity and variety of democratic options in protracted elections have outpaced voters' attention spans and cognitive capacities. These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections. This paper is mainly based on the 2022 US election.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

ces2022 |>
  ggplot(aes(x = race, fill = voted_for)) +
  stat_count(position = "dodge") +
  geom_text(stat='count', aes(label=..count..), position=position_dodge(width=0.9), vjust=-0.25, color="black") +
  facet_wrap(facets = vars(gender4)) +
  theme_minimal() +
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```
The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues. This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S. electorate. The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.

To better understand the American election and its voting system that occurred in 2022, we need to follow these steps:

Define the population: The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022. Individual respondents participate in the survey, which is designed to record various information related to electoral behavior, political perspectives, and demographic characteristics.

Gather Data: Acquire information regarding the total number of confirmed survey cases. This dataset should include various factors such as,  election experiences, contextual data, demographic details (e.g., gender, race, education), political affiliations, and viewpoints on diverse policy matters.

Determine the Time Period: Specify the time frame to calculate when the survey object was collected. The timeframe is relevant to survey participants about their opinions, voting intentions in the 2022 election. The first period is the pre-election data collection that occurred from September 29 to November 8, 2022, and the second period is post- election data gathered from November 10 to December 15, 2022.

Calculate the Case: Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.
